%%%%%%%%%%%%%%%%
%%%  config  %%%
%%%%%%%%%%%%%%%%

\documentclass[12pt]{usenixsubmit}


\usepackage{ulem}


\usepackage{setspace}
\usepackage{verbatim}
\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{array}
\usepackage{color}
\usepackage{hyperref}
%\usepackage{appendix}
\usepackage{fancyhdr}
\usepackage{enumitem}
\usepackage{geometry}


\input{config}
\usepackage{pgf}
\usepackage{tikz}

\usepackage{pgf-umlsd}
\usepackage{soul,color}

%\setstretch{0.9}
\usetikzlibrary{arrows,shadows,positioning,automata}
%%%%%%%%%%%%%%%%
%%% document %%%
%%%%%%%%%%%%%%%%

\begin{document}

%%% cover %%%

\title{Group 2: The Remote Automobile Utility Control Protocol \\ \Large{CS544 Spring 2017, Drexel University}}

\author{
    Lewis Cannalongo \\
    lrc74@drexel.edu
    \and
     Max Mattes \\
    mm3888@drexel.edu
    \and
    Ismail Kuru \\
    ik335@drexel.edu
}
\date{\today}

\maketitle

\thispagestyle{empty}

\include{abstract}

\tableofcontents
\pagebreak

\setcounter{page}{1}

%%% content %%%

\include{serv_revision}

\include{pdu_revision}
\include{pdus_qos}
\include{dfa}
\include{extensibility}
\include{security}

%%% references %%%

%\setstretch{0.8}
%\bibliographystyle{IEEEtran}
%\bibliography{references}

%%% appendicies %%%

%\clearpage

%\input{appendicies}

\end{document}
\begin{comment}

Message definition (PDUs) 
Need better representation for message definitions. 
256 byte is a long password. Is it a password or a hash of a password, or some other type of key? 
What if authentication changes with the next protocol version, how does this message structure handles that? 


DFA
According to this DFA, the only service this protocol provides is authentication and then just pass messages along. 
Is this the intention?

 Extensibility 
Protocol version negotiation happens after authentication. 
What is the authentication changes with the next version? 
For example new hash algorithm or an extra step. 
Also, what happens when you add fields to the header?

Security
Degree of Difficulty
Look & Feel
\end{comment}